They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-12 paper.tex
Paper: genome edits

\subsubsection{Genome}
The Genome class encapsulates the data that is stored on a genome-by-genome basis, and provides most of the procedures that deal with their mutation, as well as providing conversions from their internal state to the game-useful health, speed, and damage values, as well as providing an interface to conveniently call the resulting pathfinding neural net.

@@

In Figure 7, we can see the constants that are used to scale a Zombunny's health, movement speed, and damage, which need to be set manually. The Id field is used as a unique identifier if genomes need to be looked up, and also ensures that every genome will hash differently.

>>>>

\subsubsection{Genome}
The Genome class encapsulates the data that is stored on a genome-by-genome
basis, provides most of the procedures that deal with their mutation, provides
conversions from their internal state to the game-useful health, speed, and
damage values, and provides an interface to conveniently call the resulting
pathfinding neural net.

@@

In Figure 7, we can see the constants that are used to scale a Zombunny's
health, movement speed, and damage, which need to be set manually as discussed
in the hyperparameters sections. The Id field is used as a unique identifier if
genomes need to be looked up, and also ensures that every genome will hash differently.
